Through the Eyes of the Teacher - Multimodal Exploration of Expertise Differences in the Perception of Classroom Disruptions in a Laboratory Study

### 2024-11-28 02_paper/02_study/02_expertise_paper/expertise_2024_11_18_MK.Rmd
x paper

### Self-evaluation 
```{r self-eval, echo=FALSE, results='asis'}

@@

# Create Dataset for Plotting --------------------------------------------
df_quest_long <- df_quest %>%
  rowwise() %>%
  transmute(
    Group = Group,
    `Classroom Management` = round(mean(c_across(starts_with("CM")), na.rm = TRUE), 2),
    `Disruption Handling` = round(mean(c_across(starts_with("DH")), na.rm = TRUE), 2),
    `Presence` = round(mean(c_across(starts_with("P") & !starts_with("Participant")), na.rm = TRUE), 2)  # Excluding Participant column
  ) %>%
  ungroup() %>%
  pivot_longer(!Group, names_to = "Scales Self-evaluation", values_to = "Mean")

# Plot Mean Scores by Group ----------------------------------------------
quest_plot <- df_quest_long %>%
  mutate(Group = factor(Group, levels = c("Novice", "Expert"))) %>%
  ggplot(aes(x = Group, y = Mean)) +
  geom_boxplot(aes(fill = Group), outlier.shape = NA) +
  geom_point(
    size = 1,
    alpha = 0.4,
    position = position_jitter(seed = 1, width = 0.1, height = 0.1)
  ) +
  labs(x = "", y = "Mean Scores") +
  ylim(0, 4) + 
  scale_fill_brewer(palette = "RdBu") +
  facet_wrap(~`Scales Self-evaluation`, nrow = 1, strip.position = "bottom") +
  theme_cowplot() +
  ggtitle("Self-Evaluation Scores") +
  theme(
    plot.title = element_text(size = 25, face = "bold"),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    strip.text.x = element_text(size = 8),
    axis.title.y = element_text(size = 20)
  )

@@

# T-Test and Effect Sizes ------------------------------------------------
# t-Test Function for Long Format ----------------------------------------
t_test_stats_long <- function(data, group_col, scale_filter, scale_name) {
  # Subset Data for the Specific Scale
  filtered_data <- data %>%
    filter(`Scales Self-evaluation` == scale_filter)

@@

# Perform t-Tests for Each Scale
t_test_all <- t_test_stats_long(df_quest_long, "Group", "All", "Overall")
t_test_cm <- t_test_stats_long(df_quest_long, "Group", "Classroom Management", "Classroom Management")
t_test_npvc <- t_test_stats_long(df_quest_long, "Group", "Non-/Paraverbal Communication", "Non-/Paraverbal Communication")

# Combine Results into a Single Table
t_test_results <- bind_rows(t_test_all, t_test_cm, t_test_npvc)

@@

### CLASSROOM MANAGEMENT -------------------------------------------------
# Select relevant columns and remove NAs
df_cm <- df_quest %>% select(starts_with("LM"))

# Calculate omega
omega_cm <- calculate_omega_total(df_cm, "Classroom Management")

### NON & PARAVERBAL COMMUNICATION --------------------------------------
# Select relevant columns and remove NAs
df_npvc <- df_quest %>% select(starts_with("LP"))

# Calculate omega
omega_npvc <- calculate_omega_total(df_npvc, "Non-/Paraverbal Communication")

### OVERALL TEST -----------------------------------------------------
# Select relevant columns and remove NAs
df_self_all <- df_quest %>%
  select(matches("L")) %>%
  mutate(across(everything(), as.numeric)) %>%  # Ensure numeric data
  drop_na()

# Calculate omega
omega_self_all <- calculate_omega_total(df_self_all, "Overall Evaluation")

### COMBINE RESULTS INTO AN APA-CONFORM TABLE ----------------------------
# APA-Conform Table ------------------------------------------------------
omega_results <- tibble(
  Facet = c("Overall Evaluation", "Classroom Management", "Non-/Paraverbal Communication"),
  `Omega Total` = c(omega_self_all, omega_cm, omega_npvc)
)

# Display APA-Conform Table ----------------------------------------------
kable(omega_results, caption = "Internal Consistency (Omega) for Self-evaluation") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```
## Correlations

@@

# ET-Measures (Micro-Teaching Unit) - Exclude Disruptive Person
df_aoi_numb_dur <- df_aoi %>%
  filter(TOI == "Lesson") %>%
  dplyr::select(
    Participant,
    starts_with("Total_duration_of_fixations"),
    starts_with("Number_of_fixations"),
    starts_with("Average_duration"),
    Duration_of_interval  # Ensure this variable is included
  ) %>%
  dplyr::select(
    -contains("Disruptive_Person")  # Exclude Disruptive Person
  ) %>%
  rowwise() %>%
  transmute(
    Participant,
    Duration_of_interval_min = round(Duration_of_interval / 60000, 2),
    Number_fixation_min_mtu = round(sum(c_across(starts_with("Number_of")), na.rm = TRUE) /
                                      Duration_of_interval_min, 0),
    Average_duration_mtu = round(sum(c_across(starts_with("Total_duration")), na.rm = TRUE) /
                                    sum(c_across(starts_with("Number_of")), na.rm = TRUE), 0),
    GRI_mtu = round(Average_duration_mtu / Number_fixation_min_mtu, 2)
  ) %>%
  arrange(Participant)

# ET-Measures (AOI Students) - Exclude Disruptive Person
df_aoi_stud <- df_aoi %>%
  filter(TOI == "Lesson") %>%
  dplyr::select (
    Group,
    Duration_of_interval,
    Participant,
    "Total_duration_of_fixations.Anna",
    "Total_duration_of_fixations.Bianca",
    "Total_duration_of_fixations.Carl(a)",
    "Number_of_fixations.Anna",
    "Number_of_fixations.Bianca",
    "Number_of_fixations.Carl(a)"
  ) %>%
  rowwise() %>%
  transmute(
    Group = as_factor(Group),
    Duration_of_interval_min = round(Duration_of_interval / 60000, 2),
    Duration_of_interval_sec = round(Duration_of_interval / 1000, 2),
    Participant = Participant,
    Stud_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
    Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
    Stud_number_fixation_min = round(Stud_number_fixation / Duration_of_interval_min, 2),
    Stud_number_fixation_sec = round(Stud_number_fixation / Duration_of_interval_sec, 2),
    Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, 0)
  ) %>%
  drop_na()

@@

# Step 3: Pivot the data to create a single row for each Participant
df_summary <- df_aggregated %>%
  pivot_wider(
    names_from = Disruption_Category,
    values_from = c(Total_Number_of_Fixations, Total_Duration_of_Interval_Sec),
    values_fill = 0  # Replace missing values with 0
  )

>>>>

### Self-evaluation (5 classroom management items, 3 disruption handling items, 8 presence items)
```{r self-eval_5-3-8, echo=FALSE, results='asis'}

@@

# Create Dataset for Plotting with Overall Measure --------------------------------------------
df_quest_long <- df_quest %>%
  rowwise() %>%
  transmute(
    Group = Group,
    `Classroom Management` = round(mean(c_across(starts_with("CM")), na.rm = TRUE), 2),
    `Disruption Handling` = round(mean(c_across(starts_with("DH")), na.rm = TRUE), 2),
    `Presence` = round(mean(c_across(starts_with("P") & !starts_with("Participant")), na.rm = TRUE), 2),  # Excluding Participant column
    `Overall` = round(mean(c(CM_01, CM_02, CM_03, CM_04, CM_05, DH_01, DH_02, DH_03, P_01, P_02, P_03, P_04, P_05, P_06, P_07, P_08), na.rm = TRUE), 2)  # Correct Overall value
  ) %>%
  ungroup() %>%
  pivot_longer(cols = c(`Classroom Management`, `Disruption Handling`, `Presence`, `Overall`),
               names_to = "Scales Self-evaluation", values_to = "Mean")

# Plot Mean Scores by Group ----------------------------------------------
quest_plot <- df_quest_long %>%
  mutate(
    Group = factor(Group, levels = c("Novice", "Expert")),
    `Scales Self-evaluation` = factor(`Scales Self-evaluation`, levels = c("Classroom Management", "Disruption Handling", "Presence", "Overall"))  # Reorder scales
  ) %>%
  ggplot(aes(x = Group, y = Mean)) +
  geom_boxplot(aes(fill = Group), outlier.shape = NA) +
  geom_point(
    size = 1,
    alpha = 0.4,
    position = position_jitter(seed = 1, width = 0.1, height = 0.1)
  ) +
  labs(x = "", y = "Mean Scores") +
  ylim(0, 4) + 
  scale_fill_brewer(palette = "RdBu") +
  facet_wrap(~`Scales Self-evaluation`, nrow = 1, strip.position = "bottom") +
  theme_cowplot() +
  ggtitle("Self-Evaluation Scores") +
  theme(
    plot.title = element_text(size = 25, face = "bold"),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    strip.text.x = element_text(size = 8),
    axis.title.y = element_text(size = 20)
  )

@@

# t-Test and Effect Sizes ------------------------------------------------

# t-Test Function for Long Format ----------------------------------------
t_test_stats_long <- function(data, group_col, scale_filter, scale_name) {
  # Subset Data for the Specific Scale
  filtered_data <- data %>%
    filter(`Scales Self-evaluation` == scale_filter)

  # Check if there are exactly two levels in the group
  if (length(unique(filtered_data[[group_col]])) != 2) {
    warning(paste("Skipping t-test for", scale_name, ": Group must have exactly two levels"))
    return(tibble(
      `Scale` = scale_name,
      `t-value` = NA,
      `p-value` = NA,
      `Cohen's d` = NA
    ))
  }

@@

# Perform t-Tests for Each Scale
t_test_all <- t_test_stats_long(df_quest_long, "Group", "Overall", "Overall Evaluation")
t_test_cm <- t_test_stats_long(df_quest_long, "Group", "Classroom Management", "Classroom Management")
t_test_npvc <- t_test_stats_long(df_quest_long, "Group", "Disruption Handling", "Disruption Handling")
t_test_presence <- t_test_stats_long(df_quest_long, "Group", "Presence", "Presence")

# Combine Results into a Single Table
t_test_results <- bind_rows(t_test_all, t_test_cm, t_test_npvc, t_test_presence)

@@

### CLASSROOM MANAGEMENT -------------------------------------------------
# Select relevant columns and remove NAs
df_cm <- df_quest %>% select(starts_with("CM"))

# Calculate omega for Classroom Management
omega_cm <- calculate_omega_total(df_cm, "Classroom Management")

### DISRUPTION HANDLING --------------------------------------------------
# Select relevant columns and remove NAs
df_dh <- df_quest %>% select(starts_with("DH"))

# Calculate omega for Disruption Handling
omega_dh <- calculate_omega_total(df_dh, "Disruption Handling")

### PRESENCE ------------------------------------------------------------
# Select relevant columns and remove NAs
df_presence <- df_quest %>% select(starts_with("P") & !starts_with("Participant"))

# Calculate omega for Presence
omega_presence <- calculate_omega_total(df_presence, "Presence")

### OVERALL TEST -----------------------------------------------------
# Select relevant columns and remove NAs (for overall evaluation)
df_self_all <- df_quest %>%
  select(starts_with("CM"), starts_with("DH"), starts_with("P") & !starts_with("Participant")) %>%
  mutate(across(everything(), as.numeric)) %>%  # Ensure numeric data
  drop_na()

# Calculate omega for Overall Evaluation
omega_self_all <- calculate_omega_total(df_self_all, "Overall Evaluation")

### COMBINE RESULTS INTO AN APA-CONFORM TABLE ----------------------------
# APA-Conform Table ------------------------------------------------------
omega_results <- tibble(
  Facet = c("Overall Evaluation", "Classroom Management", "Disruption Handling", "Presence"),
  `Omega Total` = c(omega_self_all, omega_cm, omega_dh, omega_presence)
)

# Display APA-Conform Table ----------------------------------------------
kable(omega_results, caption = "Internal Consistency (Omega) for Self-evaluation") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

### Self-evaluation (8 classroom management items, 8 presence items)
```{r self-eval_8-8, echo=FALSE, results='asis'}

# Data Import and Preparation --------------------------------------------
df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
  filter(LI06_05 != 201, LI06_05 != 223) %>%  # Exclude specific IDs
  mutate(
    Group = ifelse(LI06_05 < 200, "Novice", "Expert"),  # Group Definition
    Participant = LI06_05  # Add new column "Participant"
  ) %>%
  arrange(Participant) %>% 
  select(
    Participant, 
    Group, 
    LM01_01:LM01_08,  # Classroom Management and Disruption Handling combined
    LP01_01:LP01_08   # Presence
  ) %>%
  rename(
    CM_01 = LM01_01, CM_02 = LM01_02, CM_03 = LM01_03, CM_04 = LM01_04, CM_05 = LM01_05,
    CM_06 = LM01_06, CM_07 = LM01_07, CM_08 = LM01_08,  # Renaming combined columns
    P_01 = LP01_01, P_02 = LP01_02, P_03 = LP01_03, P_04 = LP01_04, P_05 = LP01_05,
    P_06 = LP01_06, P_07 = LP01_07, P_08 = LP01_08
  ) %>%
  na.omit()  # Remove NAs

# Create Dataset for Plotting with Combined Scales -------------------------
df_quest_long <- df_quest %>%
  rowwise() %>%
  transmute(
    Group = Group,
    `Classroom Management` = round(mean(c_across(starts_with("CM")), na.rm = TRUE), 2),  # Combine Classroom Management and Disruption Handling
    `Presence` = round(mean(c_across(starts_with("P") & !starts_with("Participant")), na.rm = TRUE), 2),  # Excluding Participant column
    `Overall` = round(mean(c(CM_01, CM_02, CM_03, CM_04, CM_05, CM_06, CM_07, CM_08, P_01, P_02, P_03, P_04, P_05, P_06, P_07, P_08), na.rm = TRUE), 2)  # Correct Overall value
  ) %>%
  ungroup() %>%
  pivot_longer(cols = c(`Classroom Management`, `Presence`, `Overall`),
               names_to = "Scales Self-evaluation", values_to = "Mean")

# Plot Mean Scores by Group ----------------------------------------------
quest_plot <- df_quest_long %>%
  mutate(
    Group = factor(Group, levels = c("Novice", "Expert")),
    `Scales Self-evaluation` = factor(`Scales Self-evaluation`, levels = c("Classroom Management", "Presence", "Overall"))  # Reorder scales
  ) %>%
  ggplot(aes(x = Group, y = Mean)) +
  geom_boxplot(aes(fill = Group), outlier.shape = NA) +
  geom_point(
    size = 1,
    alpha = 0.4,
    position = position_jitter(seed = 1, width = 0.1, height = 0.1)
  ) +
  labs(x = "", y = "Mean Scores") +
  ylim(0, 4) + 
  scale_fill_brewer(palette = "RdBu") +
  facet_wrap(~`Scales Self-evaluation`, nrow = 1, strip.position = "bottom") +
  theme_cowplot() +
  ggtitle("Self-Evaluation Scores") +
  theme(
    plot.title = element_text(size = 25, face = "bold"),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    strip.text.x = element_text(size = 8),
    axis.title.y = element_text(size = 20)
  )

# t-Test and Effect Sizes ------------------------------------------------
# t-Test Function for Long Format ----------------------------------------
t_test_stats_long <- function(data, group_col, scale_filter, scale_name) {
  # Subset Data for the Specific Scale
  filtered_data <- data %>%
    filter(`Scales Self-evaluation` == scale_filter)

  # Check if there are exactly two levels in the group
  if (length(unique(filtered_data[[group_col]])) != 2) {
    warning(paste("Skipping t-test for", scale_name, ": Group must have exactly two levels"))
    return(tibble(
      `Scale` = scale_name,
      `t-value` = NA,
      `p-value` = NA,
      `Cohen's d` = NA
    ))
  }

# Perform t-Tests for Each Scale
t_test_all <- t_test_stats_long(df_quest_long, "Group", "Overall", "Overall Evaluation")
t_test_cm <- t_test_stats_long(df_quest_long, "Group", "Classroom Management", "Classroom Management")
t_test_presence <- t_test_stats_long(df_quest_long, "Group", "Presence", "Presence")

# Combine Results into a Single Table
t_test_results <- bind_rows(t_test_all, t_test_cm, t_test_presence)

### CLASSROOM MANAGEMENT -------------------------------------------------
# Select relevant columns and remove NAs
df_cm <- df_quest %>% select(starts_with("CM"))

# Calculate omega for Classroom Management
omega_cm <- calculate_omega_total(df_cm, "Classroom Management")

### PRESENCE ------------------------------------------------------------
# Select relevant columns and remove NAs
df_presence <- df_quest %>% select(starts_with("P") & !starts_with("Participant"))

# Calculate omega for Presence
omega_presence <- calculate_omega_total(df_presence, "Presence")

### OVERALL TEST -----------------------------------------------------
# Select relevant columns and remove NAs (for overall evaluation)
df_self_all <- df_quest %>%
  select(starts_with("CM"), starts_with("P") & !starts_with("Participant")) %>%
  mutate(across(everything(), as.numeric)) %>%  # Ensure numeric data
  drop_na()

# Calculate omega for Overall Evaluation
omega_self_all <- calculate_omega_total(df_self_all, "Overall Evaluation")

### COMBINE RESULTS INTO AN APA-CONFORM TABLE ----------------------------
# APA-Conform Table ------------------------------------------------------
omega_results <- tibble(
  Facet = c("Overall Evaluation", "Classroom Management", "Presence"),
  `Omega Total` = c(omega_self_all, omega_cm, omega_presence)
)

# Display APA-Conform Table ----------------------------------------------
kable(omega_results, caption = "Internal Consistency (Omega) for Self-evaluation") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

## Correlations

@@

# ET-Measures (Micro-Teaching Unit) - Exclude Disruptive Person
df_aoi_numb_dur <- df_aoi %>%
  filter(TOI == "Lesson") %>%
  dplyr::select(
    Participant,
    starts_with("Total_duration_of_fixations"),
    starts_with("Number_of_fixations"),
    starts_with("Average_duration"),
    Duration_of_interval  # Ensure this variable is included
  ) %>%
  dplyr::select(
    -contains("Disruptive_Person")  # Exclude Disruptive Person
  ) %>%
  rowwise() %>%
  transmute(
    Participant,
    Duration_of_interval_min = round(Duration_of_interval / 60000, 2),
    Number_fixation_min_mtu = round(sum(c_across(starts_with("Number_of")), na.rm = TRUE) /
                                      Duration_of_interval_min, 0),
    Average_duration_mtu = round(sum(c_across(starts_with("Total_duration")), na.rm = TRUE) /
                                    sum(c_across(starts_with("Number_of")), na.rm = TRUE), 0),
    GRI_mtu = round(Average_duration_mtu / Number_fixation_min_mtu, 2)
  ) %>%
  select(Participant,
        Number_fixation_min_mtu,
        Average_duration_mtu,
        GRI_mtu) %>% 
  arrange(Participant)

# ET-Measures (AOI Students) - Exclude Disruptive Person
df_aoi_stud <- df_aoi %>%
  filter(TOI == "Lesson") %>%
  dplyr::select (
    Group,
    Duration_of_interval,
    Participant,
    "Total_duration_of_fixations.Anna",
    "Total_duration_of_fixations.Bianca",
    "Total_duration_of_fixations.Carl(a)",
    "Number_of_fixations.Anna",
    "Number_of_fixations.Bianca",
    "Number_of_fixations.Carl(a)"
  ) %>%
  rowwise() %>%
  transmute(
    Group = as_factor(Group),
    Duration_of_interval_min = round(Duration_of_interval / 60000, 2),
    Duration_of_interval_sec = round(Duration_of_interval / 1000, 2),
    Participant = Participant,
    Stud_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
    Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
    Stud_number_fixation_min = round(Stud_number_fixation / Duration_of_interval_min, 2),
    Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, 0)
  ) %>%
  select(Participant,
         Stud_number_fixation_min,
         Average_duration_stud
         ) %>% 
  arrange(Participant) %>% 
  drop_na()

@@

# Step 3: Pivot the data to create a single row for each Participant
df_summary <- df_aoi_numb_disrup %>%
  pivot_wider(
    names_from = Disruption_Category,
    values_from = c(Total_Number_of_Fixations, Total_Duration_of_Interval_Sec),
    values_fill = 0  # Replace missing values with 0
  )
